Distinguishing Spin-Aligned and Isotropic Black Hole Populations With Gravitational Waves

### 2017-05-24 paper/AlignedIsotropicGW.tex
Close #35, added references suggested around kicks and commented on correlation between rates and kicks.

The spin directions in isolated
binaries\cite{TutukovYungelson:1973,TutukovYungelson:1993,Lipunov:1997,2016Natur.534..512B,Stevenson:2017,MandeldeMink:2016,Marchant:2016}
are usually expected to be preferentially aligned.  Despite observed
spin-orbit misalignments in both massive stellar
binaries\cite{Albrecht:2009,2014ApJ...785...83A} and BH X-ray
binaries\cite{Orosz:2001,Martin:2008b,Martin:2008,MorningstarMiller:2014},
mass accretion and tidal interactions will tend to realign the binary.
On the other hand, a supernova natal kick (if any) can change the
orbital plane and misalign the
binary\cite{2000ApJ...541..319K,2013PhRvD..87j4028G}; the supernova
can also tilt the spin angle, as in the double pulsar
J0737-3039\cite{2011ApJ...742...81F}; and evolutionary processes, such
as wind-driven mass loss and post-collapse fallback, can couple the
spin magnitude and direction distributions, contrary to our simplified
assumptions.  A small misalignment at wide separation can also evolve
to a more significant misalignment in component spins as the binary
spirals in through \ac{GW} emission\cite{2015PhRvD..92f4016G}, but
$\chieff$ is approximately conserved through this evolution.

>>>>

The spin directions in isolated
binaries\cite{TutukovYungelson:1973,TutukovYungelson:1993,Lipunov:1997,2016Natur.534..512B,Stevenson:2017,MandeldeMink:2016,Marchant:2016}
are usually expected to be preferentially aligned.  Despite observed
spin-orbit misalignments in both massive stellar
binaries\cite{Albrecht:2009,2014ApJ...785...83A} and BH X-ray
binaries\cite{Orosz:2001,Martin:2008b,Martin:2008,MorningstarMiller:2014},
mass accretion and tidal interactions will tend to realign the binary.
On the other hand, a supernova natal kick (if any) can change the
orbital plane and misalign the
binary\cite{2000ApJ...541..319K,2013PhRvD..87j4028G}; the supernova
can also tilt the spin angle, as in the double pulsar
J0737-3039\cite{2011ApJ...742...81F}.  Large kicks are probably
associated with reduced merger rates as more potential merging systems
are distrupted by a supernova at black hole
formation\cite{1995MNRAS.277L..35B,2002ApJ...572..962S,2003CQGra..20S..73F,2004ApJ...616..414W,2016ApJ...832L...2R}. Evolutionary
processes, such as wind-driven mass loss and post-collapse fallback,
can couple the spin magnitude and direction distributions, contrary to
our simplified assumptions.  A small misalignment at wide separation
can also evolve to a more significant misalignment in component spins
as the binary spirals in through \ac{GW}
emission\cite{2015PhRvD..92f4016G}, but $\chieff$ is approximately
conserved through this evolution.
